Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-27 abstract.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

We study the quantum quench problem for a class of bosonic conformal interfaces by computing the Loschmidt echo and the bipartite fidelity. The quench can be viewed as a sudden change of boundary conditions parameterized by $\theta$ when connecting two one-dimensional critical systems. They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface. The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartitle fidelity as $L^{-\frac{\alpha}{2}}$. We perform analytic and numerical calculation of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. Possible physical realizations of these interfaces includes for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.

>>>>

We study the quantum quench problem for a class of bosonic conformal interfaces by computing the Loschmidt echo and the bipartite fidelity. The quench can be viewed as a sudden change of boundary conditions parameterized by $\theta$ when connecting two one-dimensional critical systems. They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface. The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartitle fidelity as $L^{-\frac{\alpha}{2}}$. We perform analytic and numerical calculations of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. Possible physical realizations of these interfaces includes for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.

### 2017-06-27 analy_eval.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corner at the tip of the slit. However, without regulators the conformal invariance can rescale both to $1$ by doing a dilation transformation, thus getting rid of their dependence. Therefore, regulators are necessary in keeping track of the scale dependence, and also physically sensible when considering the lattice realization of the systems.

We thus add small semi-circles around the points where the bcc operators reside, followed by a series of conformal mapping. For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}
We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the regulator. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The vertical line at $\text{Re} w = W$ (IR regulator) is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function is 
\begin{equation}
  Z_{ab} = \langle a | e^{-\pi H } |b \rangle .
\end{equation}

The Loschmidt echo can be evaluated in the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end up with the same diagram as fidelity. With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.

@@

As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND. In the region accessible to the numerical calculation in the lattice model, we choose the process 
\begin{equation}
\label{eq:DDDD}
{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD},
\end{equation}
to verify
\begin{equation}
\label{eq:result_DDDD}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
\frac{1}{8}\ln L  &\quad\text{fidelity}  \\
\frac{1}{4}\ln t   &\quad \text{echo} ,  \\
\end{aligned} \right.  
\end{equation}
where same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}. Another process
\begin{equation}
\label{eq:DNDN}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
\end{equation}
is used to verify
\begin{equation}
\label{eq:result_DNDN}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
 (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} , \\
\end{aligned} \right. 
\end{equation}
where $\lambda = \tan \theta$ and $x = \frac{\theta}{\pi}$.

>>>>

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corner at the tip of the slit. If there is no regulator, however, a dilation transformation can rescale both to $1$ and get rid of their dependence. Therefore, regulators are necessary in keeping track of the scale dependence, and physically sensible when considering the lattice realization of the systems.

We thus add small semi-circles around the points where the bcc operators reside, followed by a series of conformal mapping. For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible locations of boundary condition changing (bcc) operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of the point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$ and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}
We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the regulator. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} .
\end{equation}
The vertical line at $\text{Re} w = W$ (IR regulator) is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. The dashed line and solid line can then be regarded as two boundary states, and the diagram corresponds to the following partition function 
\begin{equation}
  Z_{ab} = \langle a | e^{-\pi H } |b \rangle .
\end{equation}

The Loschmidt echo can be evaluated in the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end up with the same diagram as fidelity. With one more conformal mapping, it becomes the cylinder partition function between the two boundary states.

@@

As analyzed in Sec.~\ref{sec:analytic_numerics}, $S_2( \theta)$ interpolates between DD and NN, $S_1( \theta )$ interpolates between DN and ND. In the region accessible to the numerical calculation in the lattice model, we choose the process 
\begin{equation}
\label{eq:DDDD}
{\rm DD} + {\rm DD} \rightarrow  \lambda + {\rm DD},
\end{equation}
to verify
\begin{equation}
\label{eq:result_DDDD}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
\frac{1}{8}\ln L  &\quad\text{fidelity}  \\
\frac{1}{4}\ln t   &\quad \text{echo} .  \\
\end{aligned} \right.  
\end{equation}
The same results have already been obtained for $\lambda = {\rm P}$\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}. Another process
\begin{equation}
\label{eq:DNDN}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} ,
\end{equation}
is used to verify
\begin{equation}
\label{eq:result_DNDN}
\mathcal{F} = 
\left\lbrace
\begin{aligned}
 (x - x^2 )\ln L   &  \quad {\rm fidelity} \\
 2(x - x^2 ) \ln t  & \quad \text{ Loschmidt echo} , \\
\end{aligned} \right. 
\end{equation}
where $\lambda = \tan \theta$ and $x = \frac{\theta}{\pi}$.

### 2017-06-27 bd_notation.tex
[draft] Punctuation checked, may double check the following eqs. ([draft] Punctuation checked, double check the following eqs. (39), (C3), below (C12), (C27), (D9) .
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ on the two ends to $b$/ $c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) 
\end{equation}
Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$. To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation.

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} 
\end{equation}
Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

>>>>

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ prior the quench to $b$/$c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) .
\end{equation}
Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$. To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation.

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons (and our numerical simulation) corresponds to the choice of $S_1( \theta)$, and we reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} .
\end{equation}
Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This S-matrix corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

### 2017-06-27 conclusion.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

In this paper, we analyze a class of boson conformal interfaces by computing the Loschmidt echo and the bipartite fidelity.

We began by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions a concrete lattice setting.

@@

These two features are tested in three typical processes in the numerical calculation of the harmonic chains. After using suitable regulators for the zero-mode problem, the numerical results agree with the analytic calculation within error. Although tangential to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.

>>>>

In this paper, we analyzed a class of boson conformal interfaces by computing the Loschmidt echo and the bipartite fidelity.

We began by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions in a concrete lattice setting.

@@

These two features were tested in three typical processes in the numerical calculation of the harmonic chains. After using suitable regulators for the zero-mode problem, the numerical results agreed with the analytic calculation within error. Although tangential to the non-equilibrium dynamics, the fidelity calculation was used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.

### 2017-06-27 def_fidel_echo.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 ,
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface. Both of them can be produced by the imaginary time evolution. Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z,
\end{equation}

@@

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them is the groundstate of the disconnected chains and the other is groundstate evolved by the Hamiltonian of the connected chains
\begin{equation}
\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2,
\end{equation}
The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy.

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respective to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing (bcc) operator. These diagrams then become the one or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

>>>>

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 .
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface. Both of them can be produced by the imaginary time evolution. Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z.
\end{equation}

@@

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them is the groundstate of the disconnected chains and the other is the groundstate evolved by the Hamiltonian of the connected chains
\begin{equation}
\mathcal{L} \equiv |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2 .
\end{equation}
The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~\ref{fig:echo}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt echo is also the associated free energy.

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as insertion of primary field which is the (bcc) operator. These diagrams then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

### 2017-06-27 disc.tex
[draft] A few comments: 1. For the intro, could be stronger in introducing the current paper; 2. For the discussion, could be stronger in connecting to experiment (?)
Need to clarify: 1. Above Eq. 31, "iid Gaussian"? 2. Probably need to rewrite 3rd paragraph in conclusion.

In the computations we have done, the fidelity results can be converted to that of the Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$. The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips. Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces. Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can't be connected even by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

% x dependence, DN -> ND agrees with existing result;
More interesting is when the boundary conditions are of the same type, in which case we verified the quadratic angle dependence numerically for this process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
\end{equation}
The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used). This is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation. The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as the twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N. This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$. In a rational boson theory, the number of primary fields is finite. It requires further study to identify these bcc operators and explore their physical significance.

Our numerical study also shows that the far end boundary condition $c$, which in the large system size limit should not impact the system, {\it does change} the scaling dimension in a way that is not captured by our analytic computation. This is because the boundary condition on the far end may introduce additional bcc operators and thus change the free energy. It would be interesting to have a CFT calculation that reproduces the better numerical result of
\begin{equation}
{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
\end{equation}
shown in Fig.~\ref{fig:PDN_fit}.

@@

This set of boundary conditions can be realized by connecting two compact bosons. There are already numerous theoretical and experimental work on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twist the two independent bosons (two left modes plus two right modes) on the two sides. An X-ray edge singularity experiment in a quantum wire system, which uses ion to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.

>>>>

In the computations we have done, the results of fidelity can be converted to that of Loschmidt echo by the recipe $ \ln L \rightarrow 2 \ln \tau$. The numerical factor $2$ comes from the fact that the Loschmidt echo has two slit tips. Other than that, we see that they probe the same finite size effect of the free energy associated with the new interfaces. Our purpose of computing the (simpler) fidelity is diagnostic and so in the following we will mainly discuss the echo properties.

% analytic results type 1 -> type 2, c/4; 
In the Sec.~\ref{sec_sub:analy_eval}, we have presented the analytic results for the general process (assuming the far end boundary condition $c$ is the same as prior-quench interface $a$) 
\begin{equation}
 S_i( \theta_1 ) \rightarrow S_j( \theta_2 ),
\end{equation}
We find that if the conformal interfaces are of different types, i.e. $i \ne j$, the (long time) free energy is always $\frac{1}{4} \ln t$, regardless of the theta angles. The two types of conformal interface do not talk to each other because they impose on different fields. If we treat $S_1$ as a combination of Dirichlet and Neumann boundary conditions imposed on the rotated $\phi$ fields as in Eq.~\eqref{eq:rotation_a_basis}, then $S_2$ imposes one of them on the duel field of $\phi$. In the derivation of the $M$ matrix, these two correspond to the parts of the Lorentz group and can not be connected even by taking singular value of $\lambda$. It is then reasonable to find an universal echo between them. The special value of ${\rm DD} \rightarrow P$ also agrees with the existing general CFT result of completely transparent interface\cite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014}.

% x dependence, DN -> ND agrees with existing result;

For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for this process 
\begin{equation}
{\rm DN} + {\rm DN} \rightarrow \lambda + {\rm DN} . 
\end{equation}
The process gives a series of new bcc operator dimensions of the $c = 2$ boson boundary CFT. Our numerical curve of the Loschmidt echo is not as perfect as the fidelity calculation (where smaller shift regulator can be used). Such discrepancy is very likely due to the existence of the free boson zero mode, as moving away from massless point remedies the situation. The special case of ${\rm DN} \rightarrow {\rm P}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference of this exponent $\frac{3}{8}$ and the ${\rm DD} \rightarrow {\rm P}$ one of $\frac{1}{4}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N. This picture is complete in this full ${\rm DN}$ to $\lambda $ transition, where other possible primary fields fuse DN into $\lambda$. In a rational boson theory, the number of primary fields is finite. It requires further study to identify these bcc operators and explore their physical significance.

Our numerical study also shows that the far end boundary condition $c$, which in the large system size limit should not impact the system, {\it does change} the scaling dimension in a way that is not captured by our analytic computation. The reason is that the boundary condition on the far end may introduce additional bcc operators and thus change the free energy. It would be interesting to have a CFT calculation that reproduces the better numerical result of
\begin{equation}
{\rm DN} + {\rm P} \rightarrow \lambda + {\rm P} 
\end{equation}
shown in Fig.~\ref{fig:PDN_fit}.

@@

This set of boundary conditions can be realized by connecting two compact bosons. There are already numerous theoretical and experimental works on the boundary conditions of a Luttinger liquid\cite{schmeltzer_zero_1999,anfuso_luttinger_2003,voit_bounded_2000,fabrizio_interacting_1995,egger_applying_1998}, which is the universal compact boson theory of the (bosonized) one-dimensional electron gas\cite{giamarchi_quantum_2015}. For example, gate voltage \cite{egger_applying_1998} may be used to twist the left and right modes of the boson to create a boundary condition interpolating between the normal open and fixed boundary conditions. The interface studied in this paper is a generalization which (in the folding picture) twists the two independent bosons (two left modes plus two right modes) on the two sides. An X-ray edge singularity experiment in a quantum wire system, which uses ions to switch on and off the boson interfaces should be plausible to detect the exponent found in this paper.
